---
title: "compas_explorations"
output: html_document
---
```{r libraries, include=FALSE}
library(RSQLite)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(grid)
library(gridExtra)
```
Converting compas db into a csv with rsqlite
{r setup, include=FALSE}
compas <- "compas.db"
sqlite.driver <- dbDriver("SQLite")
db <- dbConnect(sqlite.driver, dbname = compas)

dbListTables(db)
mytable <- dbReadTable(db, "compas")

write.csv(mytable, file = "compas.csv")

#uncleaned by propublic acompas.db data
raw_compas <- read.csv("compas.csv")
```{r compasdata}
two_years_violent <- read.csv("C:/Users/kerim/GitHub/compas_analysis/data_propublica/compas-scores-two-years-violent.csv")
two_years_reg <- read.csv("C:/Users/kerim/GitHub/compas_analysis/data_propublica/compas-scores-two-years.csv")
raw_scores <- read.csv("C:/Users/kerim/GitHub/compas_analysis/data_propublica/compas-scores-raw.csv")
scores <- read.csv("C:/Users/kerim/GitHub/compas_analysis/data_propublica/compas-scores.csv")
```
The following is me redoing the analysis done by COMPAS
-> Only keeping defendants COMPAS score within 30 days from arrest
-> is_recid -1 means there is not COMPAS case at all
-> c_charge_degree 'O' are ordinary traffic offenses so we remove it
```{r propublica-analysis}
df <- two_years_reg %>% 
  select(age, c_charge_degree, race, age_cat, score_text, sex, 
         priors_count, days_b_screening_arrest, decile_score, 
         is_recid, two_year_recid, c_jail_in, c_jail_out) %>%
  filter(days_b_screening_arrest <= 30) %>%
  filter(days_b_screening_arrest >= -30) %>%
  filter(is_recid != -1) %>%
  filter(c_charge_degree != "O") %>%
  filter(score_text != 'N/A')
```
Swapping jail in and jail out with length of stay
```{r}
df$length_of_stay <- as.numeric(as.Date(df$c_jail_out) - as.Date(df$c_jail_in))


cor(df$length_of_stay, df$decile_score)
```
Looking at basic demographics of defendants
```{r}
summary(df$age_cat)
summary(df$race)
summary(df$score_text)
summary(df$sex)
```
stabs creates a table from cross classifying factors - in this case, sex and race
```{r}
xtabs(~ sex + race, data=df)
```
Looking at the distribution of decile scores of black and white defendants
```{r}
pblack <- df %>% filter(race == "African-American") %>%
  ggplot(aes(ordered(decile_score))) +
  geom_bar() + 
  xlab("Decile Score") +
  ylim(0, 650) +
  ggtitle("Black Defendant's Decile Scores")
pwhite <- df %>% filter(race == "Caucasian") %>%
  ggplot(aes(ordered(decile_score))) +
  geom_bar() +
  xlab("Decile Score") +
  ylim(0, 650) +
  ggtitle("While Defendant's Decile Scores")
grid.arrange(pblack, pwhite, ncol=2)
```
Contingency table with COMPAS decile_score against race
```{r}
xtabs(~ decile_score + race, data=df)
```
Racial Bias in COMPAS
We are changing some variables into factors, and then run a logistic regression comparing low against high
```{r}
new_df <- df %>%
  #change degree into a factor
  mutate(crime_factor = factor(c_charge_degree)) %>%
  #change categories into a factor
  mutate(age_factor = as.factor(age_cat)) %>%
  within(age_factor <- relevel(age_factor, ref=1)) %>%
  #change race into a factor
  mutate(race_factor = as.factor(race)) %>%
  within(race_factor <- relevel(race_factor, ref=3)) %>%
  #change gender into a factor
  mutate(gender_factor = factor(sex, labels = c("Female", "Male"))) %>%
  within(gender_factor <- relevel(gender_factor, ref=2)) %>%
  #change low to lowscore, and medium-high to high score
  mutate(score_factor = factor(score_text != "Low", labels = c("LowScore", "HighScore")))

#linear model where gender, age, race, priors, crimes, and two_year recid determines score
model1 <- glm(score_factor ~ gender_factor + age_factor + race_factor 
              + priors_count + crime_factor + two_year_recid, 
              family="binomial", data=new_df)
summary(model1)
```

```{r}
summary(df$race)

df %>% filter(race=='African-American' | race == 'Caucasian') %>% nrow()
```

```{r coxdata}
#cox_parsed <- read.csv("cox-parsed.csv")
#cox_parsed_violent <- read.csv("cox-violent-parsed.csv")
```