---
title: "matching_blurb_crime"
output: html_document
---


```{r setup}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(stringr)
library(tidyr)

broward_clean_subset <- read_csv('_data_dartmouth/BROWARD_CLEAN_SUBSET.csv')
charge_id <- read_csv('_data_dartmouth/CHARGE_ID.csv')

```
The defendant is a [RACE] [SEX] aged [AGE]. 
They have been charged with: [CRIME_CHARGE_DESCRIPTION].
This crime is classified as a [CRIME_DEGREE].
They have been convicted of [PRIORS COUNT] prior crimes.
They have [JUV_FEL_COUNT] juvenile felony charges and [JUV_MISD_COUNT] juvenile misdemeanor charges on their record.

```{r}
#removed unnecessary columns
charge_id <-
  charge_id %>%
  select(charge_id, c_charge_desc, mturk_charge_name)

#replaced charge_id number with charge description
df <-
  merge(broward_clean_subset, charge_id, by = "charge_id")

#removed the id, and the original description
df <-
  df %>%
  select(-c_charge_desc, -charge_id)

df$race <- 
  case_when(df$race == '1' ~ 'white', 
            df$race == '2' ~ 'black', 
            df$race == '3' ~ 'hispanic', 
            df$race == '4' ~ 'asian',
            df$race == '5' ~ 'native american')

df$sex  <-
  case_when(df$sex == '0' ~ 'male',
            df$sex == '1' ~ 'female')

df$`charge_degree (misd/fel)` <-
  case_when(df$`charge_degree (misd/fel)` == '1' ~ 'felony',
            df$`charge_degree (misd/fel)` == '0' ~ 'misdemeanor')
```

The defendant is a [RACE] [SEX] aged [AGE]. 
They have been charged with: [CRIME_CHARGE_DESCRIPTION].
This crime is classified as a [CRIME_DEGREE].
They have been convicted of [PRIORS COUNT] prior crimes.
They have [JUV_FEL_COUNT] juvenile felony charges and [JUV_MISD_COUNT] juvenile misdemeanor charges on their record.

```{r}
df$s1 <- 
  paste("The defendant is a", df$race, df$sex, "aged", df$age, sep=" ")
df$s2 <-
  paste("They have been charged with:", df$mturk_charge_name, sep=" ")
df$s3 <-
  paste("This crime is classified as a", df$`charge_degree (misd/fel)`, sep= " ")
df$s4 <-
  paste("They have been convicted of", df$priors_count, "prior crimes", sep = " ")
df$s5 <-
  paste("They have", df$juv_fel_count, "juvenile felony charges and", df$juv_misd_count, "juvenile misdemeanor charges on their record.", sep = " ")

new_df <- df
```
Need to store 'block', 'id', 'blurb', 'two_year_recid'
```{r}
new_df <-
  new_df %>%
  select(block_num, id, s1, s2, s3, s4, s5, two_year_recid)

new_df$blurb <-
  paste(new_df$s1, new_df$s2, new_df$s3, new_df$s4, new_df$s5, sep = ". ")

new_df$question <-
  "Do you think this person will commit another crime within 2 years?"

new_df$blurb <-
  paste(new_df$blurb, new_df$question, sep = ' ')

new_df <-
  new_df %>%
  select(block_num, id, blurb, two_year_recid)

new_blurbs <- new_df

save(new_blurbs, file = 'new_blurbs.Rda')
```