---
title: "updated mapping"
output: html_document
---
Notes:
#1 Don't bother with images for people 56+.  
We can just use a blank silhouette for those people 
since our face dataset doesn't have older people in it.

#2 Shift the age groupings slightly
3: (35, 42] *change to 45*
4: (42, Inf] *change to 46-55*
5: 56+ (NO IMAGES)

#3 *I think* that will leave us with:
For the 35-45 age group, only use images age 35-39
For the 45-55 age group, use images age 40+
You will need to add 1 or more 2 images to the 35-45 age group 
    (for black males and white males), but it looks like there are extra in the dataset
You should be ok now with the older black defendants.
We might still be short a couple of images of white'
    defendants in block #7 (short 3), and block #13 (short 1).

```{r include=FALSE}
library(tidyverse)
```
Cleaning faces dataset leaving only 
  ID
  Race
  Sex
  Age Category
```{r faces}
#reading in the data and formatting the column headers
faces <- read.csv('D:/Programs/GitHub/compas_analysis/_data_faces/faces_data.csv')

faces <- faces %>% select(ï..Target, Race, Gender, Age)
colnames(faces) <- c('target','race','sex','age')
faces$age <- round(faces$age)

#cutting the breaks of the ages 
faces$cat <-
    cut(faces$age, 
    breaks = c(0, 21, 28, 35, 39, Inf), 
    labels = c('0', '1', '2', '3', '4'))

faces$sex <- 
    case_when(faces$sex == 'F' ~ 1, 
              faces$sex == 'M' ~ 0)

faces$race <- 
    case_when(faces$race == 'A' ~ 4, 
              faces$race == 'B' ~ 2, 
              faces$race == 'L' ~ 3, 
              faces$race == 'W' ~ 1)

faces <- 
    faces %>% 
    mutate(sex = as.factor(sex), race = as.factor(race))

faces <- 
    faces %>% 
    select(-age)
```
Cleaning the defendants dataset leaving only the
  Target ID
  Race
  Sex
  Age Category
```{r defendants}
all_defendants <- read.csv('D:/Programs/GitHub/compas_analysis/_data_dartmouth/BROWARD_CLEAN_SUBSET.csv')

def <- 
    all_defendants %>% 
    select(id, race, sex, age)

def$cat <- 
    cut(def$age, 
    breaks = c(0, 21, 28, 35, 45, 55, Inf), 
    labels=c('0', '1', '2', '3', '4', '5')) 

def <- 
    def %>% 
    mutate(id = as.factor(id), race = as.factor(race), sex = as.factor(sex))

def <- def %>% select(-age)

block <- 
    all_defendants  %>% 
    select(id, block_num)

block <- 
    block %>% 
    mutate(id = as.factor(id))
```

```{r}
#adding one column with combined features
faces2 <-
  faces %>%
  mutate(features = paste(sex, cat, race, sep = '-')) %>%
  select(-sex, -cat, -race)

def2 <-
  def %>% 
  mutate(features = paste(sex, cat, race, sep = '-')) %>%
  select(-sex, -cat, -race)

#adding block for defendant identification
def2 <-
  left_join(def2, block, by = 'id')

#adding index to match faces and defendants
faces2 <-
  faces2 %>%
  group_by(features) %>%
  mutate(index = 1:n())

def2 <-
  def2 %>%
  group_by(block_num, features) %>%
  mutate(index = 1:n())

#combining both based on features and index
df_map2 <-
  full_join(def2, faces2, by = c('features', 'index'))

#filling 56+ defendants with missing targets
df_map2$target <- as.character(df_map2$target)
df_map2$target[is.na(df_map2$target)] = 'empty.png'
df_map2$target <- as.factor(df_map2$target)

#omitting na values
df_map2 <- na.omit(df_map2)

#removing index cause it don't matter yo
final_map <-
  df_map2 %>%
  select(-index)

#reordering columns for the last dataframe
final_map <-
  final_map[c("features", "block_num", "id", "target")]

save(final_map, file = 'final_map.Rda')
```